---
title: "Tweets From Bill Gates"
author: "Ashutosh Nanda"
date: "Tuesday, January 27, 2015"
output: html_document
---

##Introduction

This short post covers getting data from Twitter and making a simple histogram visualization. The code relevant to this project can be found on [my Github](https://github.com/ashutoshnanda/tweetsfrombillgates).

##Getting Twitter Data through twitteR

There is a great package called `twitteR` that allows R to interact with the massive data store of Twitter. First, we need to authenticate our session; I have already done the authentication process using `ROAuth`, which I'll load here.

```{r load-authentication}
load('twitter_authentication.Rdata')
```

Now, we can start interacting with Twitter once we load the `twitteR` package and register the OAuth credentials to the R session.

```{r load-register-twitter, message = FALSE, warning = FALSE}
library('twitteR')
registerTwitterOAuth(cred)
```

We can finally search for the tweets that @BillGates has sent out by using the following code:

```{r get-tweets}
tweets.from.billgates <- twListToDF(userTimeline('BillGates', n = 3200, 
                                                 cainfo = 'cacert.pem'))
nrow(tweets.from.billgates)
```
 
Cool, we have gathered 830 tweets from @BillGates! Here's a histogram of the favorite counts for his tweets:

```{r favorite-count-hist}
hist(tweets.from.billgates$favoriteCount, main = "Tweets by @BillGates", breaks = 25,
     xlab = "Number of times tweet was favorited", ylab = "Count", col = "black")
```

Thanks for reading, and happy Twitter mining!